TDM: Training data-based Model for \\ Dynamic Formation of Web services Communities

### 2014-12-04 papers/webservice-coalition-learning/webservice_coalition_learning.tex
changes

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{A Distributed Mechanism for Intelligent \\ Web Service Community Formation}
%
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%
%
%\IEEEcompsocitemizethanks is a special \thanks that produces the bulleted
% lists the Computer Society journals use for "first footnote" author
% affiliations. Use \IEEEcompsocthanksitem which works much like \item
% for each affiliation group. When not in compsoc mode,
% \IEEEcompsocitemizethanks becomes like \thanks and
% \IEEEcompsocthanksitem becomes a line break with idention. This
% facilitates dual compilation, although admittedly the differences in the
% desired content of \author between the different types of papers makes a
% one-size-fits-all approach a daunting prospect. For instance, compsoc
% journal papers have the author affiliations above the "Manuscript
% received ..."  text while in non-compsoc journals this is reversed. Sigh.

@@

	%\item \emph{Data Quality} The ability of a data collection to meet user requirements , defined as the proximity of a value v returned by web service to a value considered as correct. The measure of data quality is considered here as a real number in the range [0, 1], where 1 represents the most desirable score.

\end{itemize}

@@

\begin{itemize}
  \item \emph{External Parameter 1} $(exp_1)$. is an estimate of how close the web service's \emph{execution time} is to other web services. It is the difference between a web service's \emph{response time} metric and the maximum value of response time of web services, about which the web service has recently gathered information.
	\item \emph{External Parameter 2} $(exp_2)$ is a comparison of the web service's rate of performing tasks to other competing web services. It is the difference between a web service's \emph{throughput} metric and the maximum value of throughput of web services, about which the web service has recently gathered information.
\end{itemize}

@@

\begin{equation}\label{u_c_normal}
U_{C} = \big((\alpha \times (A_{C} + Et_{C}) - \beta \times (exp1_{C} + exp2_{C})\big) \times Th_{C}
\end{equation}

@@

\begin{equation}\label{u_c_load}
\begin{split}
U_{C} = \sum_{ws \in C}&\bigg(\big(\alpha \times (A_{ws} + Et_{ws}) \\
        & - \beta \times (exp1_{ws} + exp2_{ws})\big) \times Th_{ws}\bigg)
\end{split}
\end{equation}

@@

\subsection{Learning Data}\label{ss:learningdata}

@@

Having these sets built based on the training model, we are able to build a decision tree wherein each community's preferences are set, as well as the joined events that took place in different time slots. In addition to best choices, web services have access to other ordered choices and can look for the second best or third best if their first try is rejected by the target community. The consequences of each try level is analyzed in more detail in the following section, in which we launch experiments and investigate the effectiveness of the use of a decision tree with different decision layers in joining other communities and enhancing the overall utility.

\subsection{Learning Model}\label{ss:learningmodel}

@@

\subsection{DLISA Tree Creation Complexity}\label{ss:complexity}
Here we analyze the computational complexity of the DLISA decision tree creation algorithm on each time iteration $t$. Computing top $k$ preferred communities for $C_i$ in $L^t(C_i, k)$ requires an $O(n.log(n))$ sort time. $C_i$ has a result set of size $|k|$, and for each of those $k$ communities we need to check against their $k$ top preferred communities. Considering we already have the list sorted, line 6 in algorithm runs $O(k \times n.log(n))$ times. Doing this search for all communities in $|CFVS|$ set $n$ times (line 5), the overall order of complexity of the algorithm in regards with $n$ and $k$ is: $O(k^2 \times n^2.log(n))$.

>>>>

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
%\title{A Distributed Mechanism for Intelligent \\ Web Service Community Formation}
\title{TDM: Training data-based Model for \\ Dynamic Formation of Web services Communities}
%
%
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%
%
%\IEEEcompsocitemizethanks is a special \thanks that produces the bulleted
% lists the Computer Society journals use for "first footnote" author
% affiliations. Use \IEEEcompsocthanksitem which works much like \item
% for each affiliation group. When not in compsoc mode,
% \IEEEcompsocitemizethanks becomes like \thanks and
% \IEEEcompsocthanksitem becomes a line break with idention. This
% facilitates dual compilation, although admittedly the differences in the
% desired content of \author between the different types of papers makes a
% one-size-fits-all approach a daunting prospect. For instance, compsoc
% journal papers have the author affiliations above the "Manuscript
% received ..."  text while in non-compsoc journals this is reversed. Sigh.

@@

	%\item \emph{Data Quality} The ability of a data collection to meet user requirements , defined as the proximity of a value v returned by web service to a value considered as correct. The measure of data quality is considered here as a real number in the range [0, 1], where 1 represents the most desirable score.
\end{itemize}

	We normalize the range of these features so that each feature contributes approximately proportionately to the final utility outcome value. We subtract the \emph{mean} from each feature then we divide the values of each feature by its \emph{standard deviation}.

@@

\begin{itemize}
  \item \emph{External Parameter 1} $(exp_1)$. is an estimate of how close the web service's \emph{execution time} is to other web services. It is the difference between a web service's \emph{execution time} metric and the maximum value of execution time of web services, about which the web service has recently gathered information. The less value means web service has better execution time compared to other web services.
	\begin{equation}\label{exp_1:f}
		exp_1 = Et_{i} - Et_{max}
	\end{equation}
	\item \emph{External Parameter 2} $(exp_2)$ is a comparison of the web service's rate of performing tasks to other competing web services. It is the difference between a web service's \emph{throughput} metric and the maximum value of throughput of web services, about which the web service has recently gathered information. The less value means web service has better throughput compared to other web services.
	\begin{equation}\label{exp_2Lf}
		exp_2 = Th_{max} - Th_{i}
	\end{equation}
\end{itemize}

@@

\begin{equation}\label{u_c_normal}
U_{C} = \big((\alpha \times (A_{C} - Et_{C}) - \beta \times (exp1_{C} + exp2_{C})\big) \times Th_{C}
\end{equation}

The $\alpha$ and $\beta$ values are internal and external weight coefficients. Execution time and external parameters are better when they have smaller values hence the negative coefficient for them. The result is then multiplied to the throughput value $Th_{C}$, since communities are performing tasks with $Th_{C}$ rate.

@@

\begin{equation}\label{u_c_load}
\begin{split}
U_{C} = \sum_{ws \in C}&\bigg(\big(\alpha \times (A_{ws} - Et_{ws}) \\
        & - \beta \times (exp1_{ws} + exp2_{ws})\big) \times Th_{ws}\bigg)
\end{split}
\end{equation}

@@

\subsection{Data Extraction and Solution Engineering}\label{ss:learningdata}

@@

Using the $gain$ matrix and the mentioned preference ordering relations, we are able to build a decision tree where the list of possible communities to join and their expected utilities are set.
% as well as the joined events that took place in different time slots. 
In addition to best choices, web services have access to other ordered choices and can look for the second best or third best if their first try is rejected by the target community. The consequences of each try level is analyzed in more detail in the following section, in which we launch experiments and investigate the effectiveness of the use of a decision tree with different decision layers in joining other communities and enhancing the overall utility.

\subsection{Decision Profile Generation}\label{ss:learningmodel}

@@

\subsection{Decision Tree Creation Complexity}\label{ss:complexity}
Here we analyze the computational complexity of the DLISA decision tree creation algorithm on each time iteration $t$. Computing top $k$ preferred communities for $C_i$ in $L^t(C_i, k)$ requires an $O(n.log(n))$ sort time. $C_i$ has a result set of size $|k|$, and for each of those $k$ communities we need to check against their $k$ top preferred communities. Considering we already have the list sorted, line 6 in algorithm runs $O(k \times n.log(n))$ times. Doing this search for all communities in $|CFVS|$ set $n$ times (line 5), the overall order of complexity of the algorithm in regards with $n$ and $k$ is: $O(k^2 \times n^2.log(n))$.
